Capsule Based Aspect Extraction

### 2020-05-30 desc/main.tex
Models and description (#1)
* added ABAE pipe

* added CBAE model

* updated CBAE

* refactored CBAE pipeline

* updated CBAE

* added CBAE validate pipeline

* added dataset, dataset loader

* updated train pipeline

* added CBAE baseline

* 23/65/27

* added tex

* updated paper

* 11/65/53

* added worked abae

* 73/86/69

* 78/88/73

* added ABAE baseline

* CBAE 61/83/69

* CBAE 64/84/69

* updated paper

* added paper introduction

* added related work

* added model description

* added experiment template

* added CBAE results

* updated paper

* added final paper

* updated models

*

\begin{document}
\maketitle
\begin{abstract}
    In the world of data science, more and more data is required to train models. Getting labeled datasets is a very expensive and lengthy process. In this regard, in the problems of topic modeling, aspect extraction models from unstructured text are gaining popularity. These models allow, with minimal effort to annotate aspects to structure the text into a set of topics or intentions. In this paper, a comparison is made of a SotA model based on attention and the model in which the attention mechanism is replaced by a capsule network with dynamic routing.
    Codes for paper: \url{https://github.com/KirillKrasikov/TopicModelingWithCapsNet}.
\end{abstract}

>>>>

\begin{document}
\maketitle
\begin{abstract}
    In the world of data science, more and more data is required to train models. Getting labeled datasets is a very expensive and lengthy process. In this regard, in the problems of topic modeling, aspect extraction models from unstructured text are gaining popularity. These models allow, with minimal effort to annotate aspects to structure the text into a set of topics or intentions. In this desc, a comparison is made of a SotA model based on attention and the model in which the attention mechanism is replaced by a capsule network with dynamic routing.
    Codes for desc: \url{https://github.com/KirillKrasikov/TopicModelingWithCapsNet}.
\end{abstract}
